Type Safe Redis Queries: A Case Study of Type-Level Programming in Haskell

### 2017-07-25 TyDe2017/main-tyde.tex
Minor fixes before submission.
Reflect changes required by editor.

\documentclass[sigplan]{acmart}
\settopmatter{printfolios=true}

%\makeatletter\if@ACM@journal\makeatother
%% Journal information (used by PACMPL format)
%% Supplied to authors by publisher for camera-ready submission
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{1}
\acmArticle{1}
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}

%%% The following is specific to TyDe'17 and the paper
%%% 'Type Safe Redis Queries: A Case Study of Type-Level Programming in Haskell'
%%% by Ting-Yan Lai, Tyng-Ruey Chuang, and Shin-Cheng Mu.
%%%
\setcopyright{licensedothergov}
\acmDOI{10.1145/3122975.3122978}
\acmISBN{978-1-4503-5183-6/17/09}
\acmConference[TyDe'17]{2st ACM SIGPLAN International Workshop on Type-Driven Development}{September 3, 2017}{Oxford, UK}
\acmYear{2017}
\copyrightyear{2017}
\acmPrice{15.00}

@@

\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amsthm}
%\usepackage{color}
\usepackage{xcolor}
\usepackage{url}
%\usepackage{mathptmx}
\usepackage{doubleequals}
%\usepackage{makeidx}  % allows for indexgeneration
\usepackage{textcomp} % for single quote
\usepackage{fancyvrb} % for indented verbatim
\usepackage{flushend} % balance columns on last page

@@

\pagestyle{empty} %no page number
\setlength{\mathindent}{10pt}

@@

\title{Type Safe Redis Queries}
\subtitle{A Case Study of Type--Level Programming in Haskell}

\author{Ting--Yan Lai}
\authornote{Ting--Yan Lai was a summer intern from
the Inst. of Computer Science and Engineering,
National Chiao Tung Univ., Taiwan,
when part of this work was developed.}
%% \authornote is optional;
\affiliation{
%  \position{Summer Intern}
  \department{Institute of Information Science}
  \institution{Academia Sinica}
  \streetaddress{128, Academia Road, Section 2}
  \city{Nangang, Taipei City}
  \postcode{115}
  \country{Taiwan}
}
\email{banacorn@gmail.com}          %% \email is recommended

\author{Tyng--Ruey Chuang}
\affiliation{
%  \position{Associate Research Fellow}
  \department{Institute of Information Science}
  \institution{Academia Sinica}
  \streetaddress{128, Academia Road, Section 2}
  \city{Nangang, Taipei City}
  \postcode{115}
  \country{Taiwan}
}
\email{trc@iis.sinica.edu.tw}

\author{Shin--Cheng Mu}
\affiliation{
%  \position{Associate Research Fellow}
  \department{Institute of Information Science}
  \institution{Academia Sinica}
  \streetaddress{128, Academia Road, Section 2}
  \city{Nangang, Taipei City}
  \postcode{115}
  \country{Taiwan}
}
\email{scm@iis.sinica.edu.tw}

>>>>

\documentclass[sigplan, screen, 9pt]{acmart}
\settopmatter{printfolios=true}

%%% The following is specific to TyDe'17 and the paper
%%% 'Type Safe Redis Queries: A Case Study of Type-Level Programming in Haskell'
%%% by Ting-Yan Lai, Tyng-Ruey Chuang, and Shin-Cheng Mu.
%%%
\setcopyright{licensedothergov}
\acmPrice{15.00}
\acmDOI{10.1145/3122975.3122978}
\acmYear{2017}
\copyrightyear{2017}
\acmISBN{978-1-4503-5183-6/17/09}
\acmConference[TyDe'17]{2nd ACM SIGPLAN International Workshop on Type-Driven Development}{September 3, 2017}{Oxford, UK}

@@

\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{url}
\usepackage{doubleequals}
\usepackage{textcomp} % for single quote
\usepackage{fancyvrb} % for indented verbatim
\usepackage{flushend} % balance columns on last page

@@

\pagenumbering{gobble} % no page number
\setlength{\mathindent}{10pt}

@@

\title{Type Safe Redis Queries: A Case Study of Type-Level Programming in Haskell}

\author{Ting-Yan Lai}
\authornote{Ting-Yan Lai was a summer intern from
the Inst. of Computer Science and Engineering,
National Chiao Tung Univ., Taiwan,
when part of this work was developed.}
%% \authornote is optional;
\affiliation{
%  \position{Summer Intern}
  \department{Institute of Information Science}
  \institution{Academia Sinica}
  \streetaddress{128, Academia Road, Section 2}
  \city{Nangang, Taipei City}
  \postcode{115}
  \country{Taiwan}
}
\email{banacorn@gmail.com}          %% \email is recommended

\author{Tyng-Ruey Chuang}
\affiliation{
%  \position{Associate Research Fellow}
  \department{Institute of Information Science}
  \institution{Academia Sinica}
  \streetaddress{128, Academia Road, Section 2}
  \city{Nangang, Taipei City}
  \postcode{115}
  \country{Taiwan}
}
\email{trc@iis.sinica.edu.tw}

\author{Shin-Cheng Mu}
\affiliation{
%  \position{Associate Research Fellow}
  \department{Institute of Information Science}
  \institution{Academia Sinica}
  \streetaddress{128, Academia Road, Section 2}
  \city{Nangang, Taipei City}
  \postcode{115}
  \country{Taiwan}
}
\email{scm@iis.sinica.edu.tw}
